### 2025-02-14 paper/sections/other/constraints.qmd
working on key chart

function plot_db(model, x)
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(ce_data)
    yhat = [argmax(y) for y in eachcol(model(x))]
    Plots.scatter!(x[1,:], x[2,:], label="Counterfactuals", ms=15, shape=:star, color=yhat)
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")
    display(plt)
end

# Data:
constraints = [
    ["both", "both"],
    ["both", "none"]
]
```

@@

models = []

for constraint in constraints
    # Data:
    data = LinearlySeparable(
        n_train=500,
        batchsize=50,
        mutability=constraint
    )
    ce_data = get_ce_data(data)
    val_size = data.n_validation / (data.n_validation + data.n_train)
    train_set, val_set, _ = train_val_split(data, ce_data, val_size)

@@

    # Objective:
    obj = EnergyDifferentialObjective(lambda=[1.0,1.0,0.0])
    generator = GenericGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = MaxIterConvergence()

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 50,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )

    push!(models, model)
end
```

>>>>

function plot_db(model, x; _xlab="Existing Debt", _ylab="Age")

    xlab = _constraint[1] == "both" ? "$(_xlab) (mutable)" : "$(_xlab) (immutable)"
    ylab = _constraint[2] == "both" ? "$(_ylab) (mutable)" : "$(_ylab) (immutable)"

    # Data and decision boundary:
    coeff = get_log_reg_params(model)
    db = get_decision_boundary(coeff)
    plt = Plots.scatter(ce_data, label=["1=Default" "2=No Default"], xlab=xlab, ylab=ylab, title="Iteration $(_itercount)")
    Plots.abline!(plt, db.slope, db.intercept; lw=5, label="Dec. Boundary")

    # Counterfactuals:
    if !any(isnothing.(x))
        yhat = [argmax(y) for y in eachcol(model(x))]
        Plots.scatter!(x[1,:], x[2,:], label=["CE (y⁺=1)" "CE (y⁺=2)"], ms=15, shape=:star, color=yhat, group=yhat)
    end
    display(plt)

    if _itercount == 1
        push!(_plts, plt)
    end
    global _itercount += 1
end

# Data:
specs = [
    (VanillaObjective(needs_ce=true), ["both", "both"]),
    (EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "both"]),
    (EnergyDifferentialObjective(lambda=[1.0,1.0,0.0]), ["both", "none"]),
]
```

@@

models = []
plts = []

for (obj, constraint) in specs

    # Globals for the callback:
    global _constraint = constraint
    global _plts = []
    global _itercount = 1

    # Data:
    data = LinearlySeparable(
        n_train=500,
        batchsize=50,
        mutability=constraint
    )
    global ce_data = get_ce_data(data)
    val_size = data.n_validation / (data.n_validation + data.n_train)
    train_set, val_set, _ = train_val_split(data, ce_data, val_size)

@@

    # Objective:
    generator = GenericGenerator()
    opt_state = Flux.setup(Descent(), model)
    conv = MaxIterConvergence()

    model, logs = counterfactual_training(
        obj,
        model,
        generator,
        train_set,
        opt_state;
        val_set = val_set,
        nepochs = 10,
        mutability = Symbol.(constraint),
        callback = plot_db,
        nce=50,
        convergence=conv, 
    )

    push!(models, model)
    push!(_plts, current())
    push!(plts, _plts)
end
```
